R Notebook

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

@@

# View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

@@

colnames(passIt)
#####

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3,4)
                       )
colnames(passIt)
#####

@@

# Network: Creating network Data
```{r NETWORK: Network Formation}
passIt <- smugCovIdx
dim(passIt)
  #####
        #### Edgelist: Network Formation
            ## NOTE: Edgelist Format
#####
            ## network data is nx2 (or more with edge attributes)
            ## first column is "From", 
            ## second column is "To"
  #####
          ### Edgelist: inspect column names
              ## inspect column names as 3rd-kth columns of network_data may include network attributes

colnames(passIt)

@@

```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}

 smug_unrIg <- smugCovIdx

smug_unrIg <-
  graph.data.frame(
    smug_unrIg[,1:3],
    directed = F)

summary(smug_unrIg)

##### Summary Output
#####
      # IGRAPH c6de075 UN-- 274 672 -- 
      # + attr: name (v/c), ingType (e/c)

```{r Edgelist: Statnet Network Object}

#Lets read the data into the enviroment.
#This will import it formatted as an edgelist

@@

colnames(source_netEdge)
# dnkName <- "dnkName" 
# dnkIng <- "dnkIng"  
# edgeAT <- "ingType"

#Lets create an statnet object from our edgelist
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist')
  )

@@

sourceEL_sn%v%"dnkName"<- 
  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkIng)]

print(sourceEL_sn)

# it's a bloody statnet edgelist 
```

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

#### class of an object
class()

# list the structure of smugCovIdx
str()

# class of an object (numeric, matrix, data frame, etc)
class()

# list the variables in smugCovIdx
names()

colnames( )

summary( )

@@

#     provides a description of several critical network features
    print(flo.stat)

@@

    flo.ig<-
      graph.adjacency(
      flo,
      mode="undirected"
      ) 
    print(flo.ig)
```

@@

#     Count Vertices
    vcount(flo.ig)

#     Count Edges
    ecount(flo.ig)

# Is this a Bipartite or single mode network?
    is_bipartite(flo.ig)

#  Are edges directed or undirected?
    is_directed(flo.ig)

#Are edges weighted or unweighted?
    is_weighted(flo.ig)

@@

#     access vertex attributes
  head(flo.stat %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(flo.stat)

#     access edge attribute
  head(flo.stat%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(flo.stat)

#   summarize numeric network attribute
  summary(flo.stat  %v% "name")

@@

#     access vertex attribute 
  V(flo.ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(flo.ig)

#     access edge attribute
  E(flo.ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(flo.ig)

#   summarize numeric network attribute
  summary(E(flo.ig)$weight)

@@

#     Calculate distances between two nodes
    distances(flo.ig,"Bischeri","Ridolfi")

#     Calculate distance between two nodes using unweighted edges
    distances(flo.ig,"Bischeri", "Castellani",weights=NA)

@@

#     isolating the distances between specific node
    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

@@

#     find average shortest path for network
    average.path.length(flo.ig,directed=F)

@@

    sna::dyad.census(flo.stat)

@@

  igraph::dyad.census(flo.ig)

@@

#     Classify all Triad in the network: Directed Network
  sna::triad.census(flo.stat, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(flo.stat, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(flo.stat, mode="graph"))

@@

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(flo.ig)

@@

#     network transitivity:
    transitivity(flo.ig)

#     weighted network transitivity:
#   igraph::transivity(flo.ig)

@@

#     Directed Networks transitivity:
  gtrans(flo.stat)

@@

#     Retrive a list of the vertices we are interested
    V(flo.ig)[c("Bischeri" ,
                "Castellani", 
                "Medici",
                "Ridolfi")]

#     check ego network transitivity
transitivity(flo.ig,
             type="local", 
             vids=V(flo.ig)
             [c("Bischeri",
                "Castellani", 
                "Medici",
                "Ridolfi")]) 
#     get global clustering cofficient
  transitivity(flo.ig, type="global")

#     get average local clustering coefficient
  transitivity(flo.ig, type="average")

@@

> Distill is a publication format for scientific
> and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at
> <https://rstudio.github.io/distill>. ##

>>>>

```{r}
vectordata=as.vector(mtrxIt)
print(smugCov_ntWrk)
```

@@

View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

@@

#####

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3)
                       )
colnames(passIt)
#####

@@

# Network: Creating network Data
```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
colnames(smugCovIdx )

# [1] "dnkName" "dnkIng"  "ingType"
# V1 <- "dnkName" 
# V2 <- "dnkIng"  
# EA <- "ingType"
dr_smugCov <- smugCovIdx

 ##If data are in edgelist format (A) and are undirected (B), use the following command:#

#igraph object 
network_ig<- graph.edgelist(as.matrix(smugCovIdx[1:2]), directed=F)

#  Adding edge and node attributes to network/graph object

#If you have edgelist data, edge attributes will often be stored in same data file
#iGraph will read in all edge attributes automatically, inspect as follows
edge_attr(network_ig)

##but to create new edge attribute if edges sorted correctly
# E(network_ig)$COLNAME<-edge.attribute$COLNAME

#The vertex names in this file must exactly match those in the network#
#sometimes this requires using as.character(x) to change from factor to character
#create vertex attributes in igraph
# V(network_ig)[match(V(network)$name,vertex_attributes$VERTEX_NAME)]$COLNAME<-
#  vertex_attributes$COLNAME

@@

```{r NETWORK EDGELIST: Statnet & Igraph, include=FALSE}
#Lets read the data into the enviroment.
#This will import it formatted as an edgelist

@@

colnames(source_netEdge)
# [1] "dnkName" "dnkIng"  "ingType"
# V1 <- "dnkName" 
# V2 <- "dnkIng"  
# EA <- "ingType"

# Lets create an statnet object from our edgelist
#####
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist')
  )

@@

sourceEL_sn%v%"dnkName"<- 
  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkIng)]
      #####
            summary(sourceEL_sn)
dim(sourceEL_sn)

              # it's a bloody statnet edgelist !!!

#**igraph** version of the network
#####
          # NOTE: igraph automatically adds edge attributes, but not vertices

    #First let's create the object.

sourceEL_ig <- smugCovIdx

sourceEL_ig <- graph_from_data_frame(d = sourceEL_ig, directed = FALSE)

 #**igraph** Generate Edgelist

V(sourceEL_ig)$dnkName<-
  temp$dnkIng[
    match(V
          (sourceEL_ig)$name,
          temp$dnkIng)
  ]
print(sourceEL_ig )
edge_attr(sourceEL_ig)

#########
########
          smugEL_sn  <- sourceEL_sn
          smugEL_ig <- sourceEL_ig
dim(smug_sn)
```

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}

#**Statnet EdgeList**   smugEL_sn
#####
#### class of an object
class(smugEL_sn )
class(smugEL_ig )

# list the structure of smugCovIdx
str(smugEL_sn )
str(smugEL_ig )

View(smug_sn)
View(smug_ig)
```

@@

#     provides a description of several critical network features
    print(source.stat)

@@

    source.ig<-
      graph.adjacency(
      flo,
      mode="undirected"
      ) 
    print(source.ig)
```

@@

#     Count Vertices
    vcount(source.ig)

#     Count Edges
    ecount(source.ig)

# Is this a Bipartite or single mode network?
    is_bipartite(source.ig)

#  Are edges directed or undirected?
    is_directed(source.ig)

#Are edges weighted or unweighted?
    is_weighted(source.ig)

@@

#     access vertex attributes
  head(source.stat %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(source.stat)

#     access edge attribute
  head(source.stat%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(source.stat)

#   summarize numeric network attribute
  summary(source.stat  %v% "name")

@@

#     access vertex attribute 
  V(source.ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(source.ig)

#     access edge attribute
  E(source.ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(source.ig)

#   summarize numeric network attribute
  summary(E(source.ig)$weight)

@@

#     Calculate distances between two nodes
    distances(source.ig,"node 1","node 2")

#     Calculate distance between two nodes using unweighted edges
    distances(source.ig,"node 1", "node 5",weights=NA)

@@

#     isolating the distances between specific node
    all_shortest_paths(source.ig,"node 3","node 4", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

@@

#     find average shortest path for network
    average.path.length(source.ig,directed=F)

@@

    sna::dyad.census(source.stat)

@@

  igraph::dyad.census(source.ig)

@@

#     Classify all Triad in the network: Directed Network
  sna::triad.census(source.stat, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(source.stat, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(source.stat, mode="graph"))

@@

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(source.ig)

@@

#     network transitivity:
    transitivity(source.ig)

#     weighted network transitivity:
#   igraph::transivity(source.ig)

@@

#     Directed Networks transitivity:
  gtrans(source.stat)

@@

#     Retrive a list of the vertices we are interested
    V(source.ig)[c("node 1" ,
                "node 5", 
                "node 6",
                "node 2")]

#     check ego network transitivity
transitivity(source.ig,
             type="local", 
             vids=V(source.ig)
             [c("node 1",
                "node 5", 
                "node 6",
                "node 2")]) 
#     get global clustering cofficient
  transitivity(source.ig, type="global")

#     get average local clustering coefficient
  transitivity(source.ig, type="average")

@@

Distill is a publication format for scientific
and technical writing, native to the web.
>
Learn more about using Distill for R Markdown at
<https://rstudio.github.io/distill>. ##
